---
title: "Overview"
author: 
  - "Matthias Grenié"
  - "Hugo Gruson"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Overview}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---


```{r setup, include = FALSE}
library(vcr)

vcr_configure("../inst/")

use_cassette("vignette_cassette", {
  rromeo::rr_journal_issn("1947-6264")
  rromeo::rr_journal_name("Biogeography", qtype = "contains")
  rromeo::rr_journal_name("Biostatistics", qtype = "contains", multiple = TRUE)
})

insert_cassette("vignette_cassette")
```

```{r}
library(rromeo)
```

# Get summary data

Let's try to access summary data for . We can access this data using its full
name or its unique ISSN identifier.

```{r}
rr_journal_issn("1947-6264")
```

You can also search for partial matches.

```{r}
rr_journal_name("Biogeography", qtype = "contains")
```

If rromeo finds multiple journals matching your query terms, it will only return
the list of titles and ISSN by default.

You can then use this list to select the exact journal you are looking for (in
this case, it is recommended to use the ISSN).

Alternatively, you may want to get data for all those journals. To achieve this,
you may enable the `multiple` option:

```{r}
res <- rr_journal_name("Biostatistics", qtype = "contains", multiple = TRUE)
tail(res, 3)
```

This tool is useful in bibliometric studies. For example, we can now have a 
visual overview of the policies of journals in a given field:

```{r bar_graph}
library("ggplot2")
theme_set(theme_minimal())

stacked_res <- stack(res[, 4:6])
ggplot(stacked_res, aes(x = ind, fill = values)) +
  geom_bar() +
  xlab(NULL)
```

```{r pie_chart}
ggplot(res, aes(x = "a", fill = romeocolour)) +
  geom_bar() + 
  coord_polar("y") +
  xlab(NULL)
```

```{r eject_cassette}
eject_cassette("vignette_cassette")
```
